Supplementary material for 'The complex network of trophic interactions in a subAntarctic Marine Protected Area

### 2023-01-24 1st_Manuscript/SupMaterial.Rmd
minor changes

The following figure and tables summarize the data we used to build the network of trophic (predator-prey) interactions for the Marine Protected Area Namuncurá - Banco Burdwood I ecosystem.
Figure 1 resumes the type and number of references reviewed. Table 1 is the complete list of trophic interactions and the references that confirm each of them. Table 2 is the species list with details on trophospecies cases (aggregated taxa).

```{r ref-plot, echo=FALSE, fig.cap="Summary of the references used to build the network of trophic (predator-prey) interactions for the MPAN-BB ecosystem."}

@@

```{r echo=FALSE, results='asis'}

@@

# Table 1. List of interactions
knitr::kable(int_good_res %>% arrange(., (Predator)), booktabs = TRUE, format = "latex", longtable = T, col.names = c("Prey","Predator","Reference", "Link"), caption = "List of predator-prey (trophic) interactions used to build the network for the Marine Protected Area Namuncurá - Banco Burdwood I ecosystem (MPAN-BB).") %>% 
  column_spec(1:3, width="2cm") %>% 
  column_spec(4, width="14cm") %>% 
  kable_styling(latex_options = c("hold_position","repeat_header"), font_size = 4) %>% 
  landscape()

@@

```{r echo=FALSE, results='asis'}

@@

# Table 2. List of species
knitr::kable(sp_list, format = "latex", booktabs = TRUE, linesep = "", longtable = TRUE, col.names = c("Species","Group","Reference","Link","Observation"), caption = "List of species for the food web of the Marine Protected Area Namuncurá - Banco Burdwood I ecosystem (MPAN-BB).") %>%
  column_spec(1:3, width="3cm") %>%
  column_spec(4:5, width="5cm") %>% 
  kable_styling(latex_options = c("hold_position", "repeat_header"), font_size = 4) %>% 
  landscape()

@@

### Species-level properties

Figure 2 shows the species topological roles of the food web for the MPA Namuncurá-Banco Burdwood ecosystem. Species, represented by circles, are coloured by role: network connector (dark purple), module connector (light pink), module hub (light green), and module specialist (dark green). Network connector = 5 species; module connector = 35 species; module hub = 7 species; and module specialist = 332 species.

```{r toprole, echo=FALSE, fig.width = 20, fig.height=20, fig.cap="Graph of the food web showing species coloured by topological role: network connector (dark purple), module connector (light pink), module hub (light green), and module specialist (dark green)."}

>>>>

The following figure and tables summarize the data we used to build the network of trophic (predator-prey) interactions for the Marine Protected Area Namuncurá - Banco Burdwood I ecosystem.
Figure 1 resumes the type and number of references reviewed. Table 1 is the complete list of trophic interactions and references that confirm each of them. Table 2 is the species list with details on trophic species cases (aggregated taxa).

```{r ref_plot, echo=FALSE, fig.cap="Summary of references used to build the network of trophic (predator-prey) interactions for the MPAN-BB ecosystem."}

@@

```{r tableS1, echo=FALSE, results='asis'}

@@

# Table 1. List of interactions
knitr::kable(int_good_res %>% arrange(., (Predator)), booktabs = TRUE, format = "latex", longtable = T, col.names = c("Prey","Predator","Reference", "Link"), caption = "List of predator-prey (trophic) interactions for the food web of the Marine Protected Area Namuncurá - Banco Burdwood I ecosystem.") %>% 
  column_spec(1:3, width="2cm") %>% 
  column_spec(4, width="14cm") %>% 
  kable_styling(latex_options = c("hold_position","repeat_header"), font_size = 4) %>% 
  landscape()

@@

```{r tableS2, echo=FALSE, results='asis'}

@@

# Table 2. List of species
knitr::kable(sp_list, format = "latex", booktabs = TRUE, linesep = "", longtable = TRUE, col.names = c("Species","Group","Reference","Link","Observation"), caption = "List of species for the food web of the Marine Protected Area Namuncurá - Banco Burdwood I ecosystem.") %>%
  column_spec(1:3, width="3cm") %>%
  column_spec(4:5, width="5cm") %>% 
  kable_styling(latex_options = c("hold_position", "repeat_header"), font_size = 4) %>% 
  landscape()

@@

Table 3 presents an exhaustive list of the species-level properties for the food web of the MPA Namuncurá - Banco Burdwood I ecosystem.

```{r tableS3, echo=FALSE}

load("../results/summary_results_jan23.rda")

# Table 2. List of species
knitr::kable(spp_total %>% 
               mutate(TopRole = case_when(TopRole == "hubcon" ~ "netcon",
                                          TRUE ~ TopRole)) %>% 
               dplyr::select(TrophicSpecies, FunctionalGroup, TotalDegree, NumPrey, NumPred, Between, Close, TL, meanTrophicSimil, TopRole) %>% 
               arrange(., desc(TotalDegree)) %>% 
               mutate(across(where(is.numeric), round, 4)), 
             format = "latex", booktabs = TRUE, linesep = "", longtable = TRUE, col.names = c("Species","Group","Degree","NumPrey","NumPred","Between","Close","TL","TS","TR"), align = "llcccccccc", caption = "Species-level properties for the food web of the Marine Protected Area Namuncurá - Banco Burdwood I ecosystem. Degree: total number of interactions; Between: betweenness; Close: closeness; TL: trophic level; TS: trophic similarity; TR: topological role (netcon = network connector, modcon = module connector, modhub = module hub, modspe = module specialist).") %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"), font_size = 4.5)

Figure 2 shows the species' topological roles in the food web graph. Species, represented by circles, are coloured by role: network connector (dark purple), module connector (light pink), module hub (light green), and module specialist (dark green). Network connector = 5 species; module connector = 35 species; module hub = 7 species; and module specialist = 332 species.

```{r toprole_graph, echo=FALSE, fig.width = 20, fig.height=20, fig.cap="Graph of the food web showing species coloured by topological role: network connector (dark purple), module connector (light pink), module hub (light green), and module specialist (dark green)."}
